### 2018-04-09 Sections/encrypted_cloud_quantum_computing.tex
Added Algo to XXII
There’s a big in the algorithm environment. Added part has been
commented out.

\sihui{The first FHE scheme was reported in Gentry's seminal paper \cite{bib:gentry2009fully}. He showed that if a homomorphic encryption scheme can evaluate its own decryption circuit, and also slightly augmented versions of it--a feature he calls {\it bootstrapping}, one can construct a FHE scheme from it. Then he constructed a homomorphic encryption protocol using ideal lattices, and via a clever transformation that decreases the complexity of its decryption circuit, showed that it is bootstrappable with respect to a universal set of gates. For a security parameter $\lambda$, Gentry's scheme has a $\widetilde{O}(\lambda^6)$ \footnote{The tilde in the big O notation means that we are ignoring logarithmic factors.} bit bound on complexity for refreshing a ciphertext corresponding to a 1-bit plaintext \cite{bib:Gentrythesis}. This was subsequently reduced to $\widetilde{O}(\lambda^{3.5})$ \cite{bib:Damien2010}, $\widetilde{O}(\lambda)$ \cite{bib:Brakerski2011}, and ${\rm polylog (\lambda)}$ for any width-$\Omega(\lambda)$ circuit with $t$ gates \cite{bib:Craig2012}. }
%
% Homomorphic Encryption
%

>>>>

\sihui{The first FHE scheme was reported in Gentry's seminal paper \cite{bib:gentry2009fully}. He showed that if a homomorphic encryption scheme can evaluate its own decryption circuit, and also slightly augmented versions of it--a feature he calls {\it bootstrapping}, one can construct a FHE scheme from it. Then he constructed a somewhat homomorphic encryption protocol using ideal lattices, and via a clever transformation that decreases the complexity of its decryption circuit, showed that it is bootstrappable with respect to a universal set of gates. For a security parameter $\lambda$, Gentry's scheme has a $\widetilde{O}(\lambda^6)$ \footnote{The tilde in the big O notation means that we are ignoring logarithmic factors.} bit bound on complexity for refreshing a ciphertext corresponding to a 1-bit plaintext \cite{bib:Gentrythesis}. This was subsequently reduced to $\widetilde{O}(\lambda^{3.5})$ \cite{bib:Damien2010}, $\widetilde{O}(\lambda)$ \cite{bib:Brakerski2011}, and ${\rm polylog (\lambda)}$ for any width-$\Omega(\lambda)$ circuit with $t$ gates \cite{bib:Craig2012}. }

A homomorphic encryption scheme is made up of four algorithms: a key generation algorithm, an encryption algorithm, an evaluation algorithm, and a decryption algorithm.
%
% Algorithm:Keygen
%
%\begin{algorithm}
%\caption{Key Generation algorithm}\label{euclid}
%\begin{algorithmic}[1]
%\Procedure{KeyGen(R, ${\bf B}_I$)}{}
%\BState \textbf{Input:} ring $R$, basis ${\bf B}_I$ of 
%a ideal $I\subset R$
%\BState \textbf{Output:} pk=($R$, ${\bf B}_I$, 
%$B_J^{\rm pk}$, {\sc Samp}), $sk={\bf B}_J^{\rm sk}$
%\State $({\bf B}_J^{\rm sk},{\bf B}_J^{\rm pk}) \gets 
%\textit{\sc IdealGen}(R, {\bf B}_I) $
%\BState \emph{top}:
%\If {$i > \textit{stringlen}$} \Return false
%\EndIf
%\State $j \gets \textit{patlen}$
%\BState \emph{loop}:
%\If {$\textit{string}(i) = \textit{path}(j)$}
%\State $j \gets j-1$.
%\State $i \gets i-1$.
%\State \textbf{goto} \emph{loop}.
%\State \textbf{close};
%\EndIf
%\State $i \gets i+\max(\textit{delta}
%_1(\textit{string}(i)),\textit{delta}_2(j))$.
%\EndProcedure
%\end{algorithmic}
%\end{algorithm}
